PM Mungbean meta-analysis

### 2021-02-01 02_Preliminary_analysis.Rmd
Remove duplicated tables

```{r FinalTrialsForInclusion1}
tmp1 <- PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   distinct(trial_ref, location, year) %>%
   arrange(year)
table(tmp1$year)
```

@@

What is the variation in yield over all the trials (including non-DMI fungicide trials) in the no spray control and fungicide treated plots.

```{r ControlYield_AllTrials}
PM_MB_dat %>%
   filter(fungicide_ai == "control") %>%
   summarise(
      mean_yield = mean(grain_yield.t.ha. * 1000),
      minimum_yield = min(grain_yield.t.ha. * 1000),
      maximum_yield = max(grain_yield.t.ha. * 1000),
      yield_stdev = sd(grain_yield.t.ha. * 1000),
      yield_SE = sd(grain_yield.t.ha. * 1000) /
         sqrt(n())
   ) %>%
   kable(align = 'c',
         caption = "Average yield statistics for no spray control plots")
```

What is the yield variation in no spray control trials yield over only the DMI fungicide trials.  
```{r ControlYield_DMITrials}
DMITrials <- PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   distinct(trial_ref) %>%
   pull()

PM_MB_dat %>%
   filter(trial_ref %in% DMITrials) %>%
   filter(fungicide_ai == "control") %>%
   summarise(
      mean_yield = mean(grain_yield.t.ha. * 1000),
      minimum_yield = min(grain_yield.t.ha. * 1000),
      maximum_yield = max(grain_yield.t.ha. * 1000),
      yield_stdev = sd(grain_yield.t.ha. * 1000),
      yield_sterr = sd(grain_yield.t.ha. * 1000) / (sqrt(length(grain_yield.t.ha.)))
   ) %>%
   kable(align = 'c',
         caption = "Average yield statistics for control plots in trials which used a DMI fungicide")
```

Mean yields in DMI fungicide treated plots
```{r Yield_DMITrials}
PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")%>%
   summarise(mean_yield = mean(grain_yield.t.ha.*1000),
             minimum_yield = min(grain_yield.t.ha.*1000),
             maximum_yield = max(grain_yield.t.ha.*1000),
             yield_stdev = sd(grain_yield.t.ha. * 1000),
             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))%>%
   kable(align = 'c',
   caption = "Average yield statistics for DMI fungicide treated plots")

@@

Trial mean yields in all fungicide treated plots
```{r Yield_AllTrials}
PM_MB_dat %>%
   group_by(trial_ref, location, year)%>%
   summarise(mean_yield = mean(grain_yield.t.ha.*1000),
             minimum_yield = min(grain_yield.t.ha.*1000),
             maximum_yield = max(grain_yield.t.ha.*1000),
             yield_stdev = sd(grain_yield.t.ha. * 1000),
             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))%>%
   arrange(yield_sterr) %>%
   kable(align = 'c',
   caption = "Average yield statistics for DMI fungicide treated plots")

>>>>

```{r FinalTrialsForInclusion1}
tmp1 <- PM_MB_dat %>%
   distinct(trial_ref, location, year) %>%
   arrange(year)
table(tmp1$year)
```

@@

What is the variation in yield over all the trials in the no spray control.

```{r ControlYield_AllTrials}
PM_MB_dat %>%
   filter(fungicide_ai == "control") %>%
   summarise(
      mean_yield = mean(grain_yield.t.ha. * 1000),
      median_yield = median(grain_yield.t.ha. * 1000),
      minimum_yield = min(grain_yield.t.ha. * 1000),
      maximum_yield = max(grain_yield.t.ha. * 1000),
      yield_stdev = sd(grain_yield.t.ha. * 1000),
      yield_SE = sd(grain_yield.t.ha. * 1000) /
         sqrt(n())
   ) %>%
   kable(align = 'c',
         caption = "Average yield statistics for no spray control plots")
```

Mean yields in DMI fungicide treated plots
```{r Yield_DMITrials}
PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")%>%
   summarise(mean_yield = mean(grain_yield.t.ha.*1000),
             median_yield = median(grain_yield.t.ha. * 1000),
             minimum_yield = min(grain_yield.t.ha.*1000),
             maximum_yield = max(grain_yield.t.ha.*1000),
             yield_stdev = sd(grain_yield.t.ha. * 1000),
             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))%>%
   kable(align = 'c',
   caption = "Average yield statistics for DMI fungicide treated plots")

@@

Trial mean yields in all fungicide treated plots
```{r Yield_AllTrials}
PM_MB_dat %>%
   group_by(trial_ref, location, year)%>%
   summarise(mean_yield = mean(grain_yield.t.ha.*1000),
             median_yield = median(grain_yield.t.ha. * 1000),
             minimum_yield = min(grain_yield.t.ha.*1000),
             maximum_yield = max(grain_yield.t.ha.*1000),
             yield_stdev = sd(grain_yield.t.ha. * 1000),
             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))%>%
   arrange(yield_sterr) %>%
   kable(align = 'c',
   caption = "Average yield statistics for DMI fungicide treated plots")
